---
title: "Results v2"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(envimaR)
if (Sys.info()[["nodename"]] == "MyComputer") {
  root_folder <- "D:/plygrnd/Sen2LUI/Sen2LUI"
} else {
  root_folder <- "D:/plygrnd/Sen2LUI/Sen2LUI"
}
source(file.path(root_folder, "src/functions/000_setup.R"))
```


## Model results

The figures show the model results depending on the overall dataset used for model training and testing (x axis) and 
the subdataset used for training (headline in plots). All plots together give an impression on how sensitive the model
is regarding the available dataset for model training and testing (i.e. which years and exploratories).

For example, the first plot on the left shows the results if data
from (i) 2017 and 2018, (ii) 2017, 2018, 2019, (iii) 2017 and 2019, and (iv) 2018 and 2019 was available for model
training and testing. The performance is computed based on a left out dataset encompassing all data from 2017.

Hence, the very left entry on the x axis (ALL_2017_2018) indicates the model performance if the model is trained on 
data from 2018 and tested on data from 2017. The very right entry on the x axis (ALL_2018_2019) does not show any 
model performance because if only data from 2018 and 2019 is available, data from 2017 cannot be left out.

```{r, echo = FALSE}
model_files <- list.files(file.path(root_folder, "data/results/models/"),
  pattern = glob2rx("*.rds"),
  full.names = TRUE
)

models <- lapply(model_files, function(m) {
  enviLoad(m)
})

model_info <- lapply(models, function(m) {
  tmp <- varImp(m$dat, scale = FALSE)$importance
  
  df_results <- data.frame(
    predictor_group = m$meta$predictor_group,
    model_run = m$meta$model_run,
    spacefolds = m$meta$spacefolds,
    rmse = m$dat$resample[order(m$dat$resample$Resample), "RMSE"],
    rsquared = m$dat$resample[order(m$dat$resample$Resample), "Rsquared"],
    predictor_number = length(m$dat$selectedvars)
  )
  
  df_predictors <- data.frame(
    predictor_group = rep(m$meta$predictor_group, nrow(tmp)),
    model_run = rep(m$meta$model_run, nrow(tmp)),
    spacefolds = rep(m$meta$spacefolds, nrow(tmp)),
    predictors = rownames(tmp),
    predictor_importance = tmp$Overall
  )

  return(list(df_results = df_results, df_predictors = df_predictors))
})
model_performance <- do.call("rbind", lapply(model_info, "[[", 1))
model_predictors <- do.call("rbind", lapply(model_info, "[[", 2))

# Add SEG_2017 (only for plot layout reasons)
fill_seg_2017 <- lapply(unique(model_performance[model_performance$spacefolds == "AEG_2017", "predictor_group"]), function(pg){
  data.frame(
    predictor_group = pg,
    model_run = unique(model_performance[model_performance$spacefolds == "AEG_2017", "model_run"]),
    spacefolds = "SEG_2017",
    rmse = NA,
    rsquared = NA,
    predictor_number = NA
  )
})
fill_seg_2017 <- do.call("rbind", fill_seg_2017)

model_performance <- rbind(
  model_performance,
  fill_seg_2017
)


spacefolds_years <- c("2017", "2018", "2019")

ggplot(
  data = model_performance[model_performance$spacefolds %in% spacefolds_years, ],
  mapping = aes(x = model_run, y = rsquared, fill = predictor_group)
) +
  geom_col(position = "dodge") +
  labs(x = "Model dataset used for training", y = expression(r^2)) +
  theme_bw() +
  theme(
    text = element_text(size = 10), axis.title = element_text(size = 10), legend.text = element_text(size = 10),
    legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 0.95, vjust = 0.2),
    legend.title = element_blank(), panel.background = element_blank(),
    panel.grid.major = element_blank(), panel.grid.minor = element_blank()
  ) +
  facet_wrap(~spacefolds)

ggplot(
  data = model_performance[!model_performance$spacefolds %in% spacefolds_years, ],
  mapping = aes(x = model_run, y = rsquared, fill = predictor_group)
) +
  geom_col(position = "dodge") +
  labs(x = "Model dataset used for training", y = expression(r^2)) +
  theme_bw() +
  theme(
    text = element_text(size = 10), axis.title = element_text(size = 10), legend.text = element_text(size = 10),
    legend.position = "none", axis.text.x = element_text(angle = 90, hjust = 0.95, vjust = 0.2),
    legend.title = element_blank(), panel.background = element_blank(),
    panel.grid.major = element_blank(), panel.grid.minor = element_blank()
  ) +
  facet_wrap(~spacefolds)
```

## Predictor importance

Mean predictor importance averaged over all model runs if importance is larger 0.

```{r, echo = FALSE}
predictor_importance <- aggregate(model_predictors$predictor_importance,
  by = list(model_predictors$predictor_group, model_predictors$predictors),
  FUN = mean
)
names(predictor_importance) <- c("Predictor_Group", "Predictors", "Importance")
predictor_importance$Predictor_Group <- factor(predictor_importance$Predictor_Group, levels = c("sat", "sat_met", "met"))
# predictor_importance[order(predictor_importance$Predictor_Group, predictor_importance$Importance, decreasing = TRUE), ]

predictor_number <- aggregate(predictor_number ~ model_performance$predictor_group, model_performance,
  FUN = mean,
  na.action = na.omit
)

# Compile predictor importance dataset for further model training and testing
predictors_sat <- predictor_importance[predictor_importance$Predictor_Group == "sat", ]
predictors_sat_met <- predictor_importance[predictor_importance$Predictor_Group == "sat_met", ]

predictors_sat_ge_10 <- predictors_sat[order(predictors_sat$Importance, decreasing = TRUE), ]
predictors_sat_ge_10[predictors_sat_ge_10$Importance >= 10, ]
predictors_sat_met_ge_10 <- predictors_sat_met[order(predictors_sat_met$Importance, decreasing = TRUE), ]
predictors_sat_met_ge_10[predictors_sat_met_ge_10$Importance >= 10, ]

meta <- createMeta("Sen2LUI")
meta$info <- "Average predictor importance from first model run."
enviSave(predictors_sat, file.path(root_folder, "data/results/info/predictors_sat_ffs.rds"), meta = meta)
enviSave(predictors_sat_met, file.path(root_folder, "data/results/info/predictors_sat_met_ffs.rds"), meta = meta)


ggplot(
  data = predictor_importance[predictor_importance$Importance >0, ],
  mapping = aes(x = Predictor_Group, y = Predictors, fill = Importance)
) +
  geom_raster() +
  labs(x = "Predictor group", y = expression(r^2)) +
  theme_bw() +
  theme(
    text = element_text(size = 8), axis.title = element_text(size = 8), legend.text = element_text(size = 8),
    legend.position = "right", axis.text.x = element_text(angle = 90, hjust = 0.95, vjust = 0.2),
    legend.title = element_blank(), panel.background = element_blank(),
    panel.grid.major = element_blank(), panel.grid.minor = element_blank()
  ) 
```
